Supplementary information for ``CLM5-PPE"

### 2024-06-10 ms/supp.tex

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figs/supp/survivability_c285.png}
\caption{Survivability.}
\label{supp:surv}
\end{figure}

@@

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figs/supp/survivability_c285.png}
\caption{Survivability in the low CO$_2$ ensemble. The sixteen natural vegetation PFTs are on the vertical axis, and the perturbation number sets the horizontal axis. A PFT is classified as dead in a given gridcell if it does not achieve an LAI of at least 0.1 m2/m2 at any point during the simulation. A PFT is classified as dead for a given perturbation if more than 30\% of the area that was alive with the default parameters is dead in the perturbed simulation.}
\label{supp:surv}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figs/supp/FCEV_global_mean.png}
\caption{Global mean canopy evaporation (FCEV) parameter rankings across the six forcing scenarios.}
\label{supp:fcev}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figs/supp/anomalies.png}
\caption{Maps of average forcing anomalies in the pre-industrial (left column) and future climate forcing (right column) simulations. Global averages over land, Antarctica excluded, are written in text on each subplot.}
\label{supp:anomalies}
\end{figure}
